PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Polishing

\usepackage{natbib}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{booktabs}

@@

\subsection{The Freeplay Sandbox}

@@

The dataset consists in a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) 25 records have been
acquired (\ie 50 children), totalling 08h41m of recording. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records. As
mentioned above, the duration of each play episode varies ($M=20m51s,
SD=10m40s$), but it is capped to a maximum of 40 minutes.

Data is collected using the ROS middleware\footnote{\url{http://ros.org}} and
recorded as \emph{bag} files. Every dataframe is timestamped.
Table~\ref{table|datastreams} lists all the recorded datastreams.

\begin{table}[]
\centering
\caption{List of datastreams stored in each record}
\label{table|datastreams}
\begin{tabular}{@{}lll@{}}
\toprule
\bf Domain  & \bf Type                              & \bf Details                          \\ \midrule
child 1     & audio                                 & 16kHz, mono, semi-directional        \\
            & face (RGB)                            & qHD (960$\times$540), 30Hz           \\
            & face (depth)                          & VGA (640$\times$480), 30Hz           \\
            & facial features                       & 68 3D points, 30Hz                   \\ \midrule
child 2     & audio                                 & 16kHz, mono, semi-directional        \\
            & face (RGB)                            & qHD (960$\times$540), 30Hz           \\
            & face (depth)                          & VGA (640$\times$480), 30Hz           \\
            & facial features                       & 68 3D points, 30Hz                   \\ \midrule
environment & RGB                                   & qHD (960$\times$540), 29.7Hz         \\ \midrule
touchscreen & background drawing (RGB)              & 4Hz                                  \\
            & touches                               & 6 points multi-touch, 10Hz           \\
            & items position and orientation        & ($x,y,\theta$), 10Hz                 \\ \midrule
annotations & \multicolumn{2}{l}{timestamped annotations of social behaviours and remarkable events}   \\ \midrule
other       & \multicolumn{2}{l}{static transforms between touchscreen and facial cameras} \\
            & \multicolumn{2}{l}{cameras calibration informations}                         \\ \bottomrule
\end{tabular}
\end{table}

As the data is recorded using ROS's bag files, it can be replayed in the exact
same conditions as it was during the recording. All the video streams use
calibrated cameras. Only the raw RGB and depth video streams are recorded.

@@

\paragraph{Hardware}
The sandtray is made of a 27" Samsung All-In-One computer running Ubuntu Linux
and equipped with a fast 1TB SSD hard-drive. The computer is held horizontal in
a custom aluminium frame standing 26cm above the ground
(Fig.~\ref{fig|freeplay}, right). All the cameras are plugged directly over
USB-3 to the computer. The computer performs all the data acquisition using ROS
Kinetic.

The children faces are recorded from two Intel RealSense SR300 RGB-D cameras
(short range, 0.2m to 1.2m, indoor RGB-D cameras), placed at the corners of the
the sandtray (Figs.~\ref{fig|rviz} and~\ref{fig|setup}), and tilted to face the
children. The cameras are rigidly mounted on custom 3D-printed brackets, and
their 6D pose with respect to the sandtray screen is precisely known and
recorded (this enables in particular accurate estimation of the children's head
pose).

Audio is recorded from the same SR300 cameras (one audio stream is recorded for
each child, from the camera facing her/him).

Finally, a third RGB camera (the RGB stream of a Microsoft Kinect One) records
the whole interaction setting. These video stream is intended to support human
coders while annontating the interaction, and is not precisely calibrated.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\linewidth]{rviz-sandtray}
    \hspace{0.2em}
    \includegraphics[width=0.48\linewidth]{3d-point-cloud-facial-features}
    \caption{The freeplay sandbox, visualised at runtime with ROS RViz. The
    current background drawing is published on a regular image
    topic and computer vision is used to segment it into zones (visible in
    the central panel, right picture). The poses of the interactive items
    are published, as well as an estimate of the children's head pose.
    The left picture shows a reconstructed 3D point cloud of one child face,
    along with the detected 68 facial features.}
    \label{fig|rviz}
\end{figure}

\paragraph{Software}
The sandbox is implemented with two frameworks: the Qt's \emph{QtQuick} framework
for the graphical interface of the game, and the \emph{Robot Operating System}
(ROS) for the modular implementation of the data processing and data acquisition
pipelines. A dedicated bridge between QtQuick and ROS has been specifically
developped to enable the game interface to export the positions of every
iteractive items as they move, the background image whenever it is painted over,
and the children's touches. The game interface is open-source and available online:
\url{https://github.com/severin-lemaignan/freeplay-sandbox-qt}.

@@

\subsection{Data post-processing}

>>>>

\usepackage{natbib}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{booktabs}
\usepackage{tablefootnote}

@@

\subsection{The Freeplay Sandbox task}

@@

The dataset consists in a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) 25 records have been
acquired (\ie 50 children), totalling 08h41m of recording. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records. As
the children decide themselves when to stop, the duration of each play episode varies ($M=20m51s,
SD=10m40s$). It is however capped to a maximum of 40 minutes.

Data is collected using the ROS middleware\footnote{\url{http://ros.org}} and
recorded as \emph{bag} files. Table~\ref{table|datastreams} lists all the
recorded datastreams.  Every dataframe is timestamped; as the data is recorded
using ROS's bag files, it can be replayed in the exact same conditions as it
has been recorded.  All the video streams use calibrated cameras; only the raw
RGB and depth video streams are stored in the dataset, section~\ref{postprocessing} discuss
how to reconstruct from them calibrated streams and 3D point clouds.

\begin{table}[]
\centering
\caption{List of datastreams stored in each record}
\label{table|datastreams}
\begin{tabular}{@{}lll@{}}
\toprule
\bf Domain  & \bf Type                              & \bf Details                          \\ \midrule
child 1     & audio                                 & 16kHz, mono, semi-directional        \\
            & face (RGB)                            & qHD (960$\times$540), 30Hz           \\
            & face (depth)                          & VGA (640$\times$480), 30Hz           \\
            & facial features\tablefootnote{\label{postprocesspass}Added to the dataset during a post-processing pass.} & 68 3D points, 30Hz                   \\ \midrule
child 2     & audio                                 & 16kHz, mono, semi-directional        \\
            & face (RGB)                            & qHD (960$\times$540), 30Hz           \\
            & face (depth)                          & VGA (640$\times$480), 30Hz           \\
            & facial features\textsuperscript{\ref{postprocesspass}} & 68 3D points, 30Hz                   \\ \midrule
environment & RGB                                   & qHD (960$\times$540), 29.7Hz         \\ \midrule
touchscreen & background drawing (RGB)              & 4Hz                                  \\
            & touches                               & 6 points multi-touch, 10Hz           \\
            & items position and orientation        & ($x,y,\theta$), 10Hz                 \\ \midrule
annotations & \multicolumn{2}{l}{timestamped annotations of social behaviours and remarkable events}   \\ \midrule
other       & \multicolumn{2}{l}{static transforms between touchscreen and facial cameras} \\
            & \multicolumn{2}{l}{cameras calibration informations}                         \\ \bottomrule
\end{tabular}
\end{table}

@@

\paragraph{Hardware}
The sandtray is made of a 27" Samsung All-In-One computer running Ubuntu Linux
and equipped with a fast 1TB SSD hard-drive. The computer is held horizontally in
a custom aluminium frame standing 26cm above the ground
(visible in Fig.~\ref{fig|freeplay}). All the cameras are plugged directly over
USB-3 to the computer. The computer performs all the data acquisition using ROS
Kinetic.

The children faces are recorded from two short range Intel RealSense SR300
RGB-D cameras (0.2m to 1.2m) placed at the corners of the the sandtray
(Figs.~\ref{fig|rviz} and~\ref{fig|setup}) and tilted to face the children. The
cameras are rigidly mounted on custom 3D-printed brackets. This enables a
precise measurement of their 6D pose relative to the touchscreen (extrinsic
calibration).

Audio is recorded from the same SR300 cameras (one audio stream is recorded for
each child, from the camera facing her).

Finally, a third RGB camera (the RGB stream of a Microsoft Kinect One) records
the whole interaction setting. These video stream is intended to support human
coders while annotating the interaction, and is not precisely calibrated.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\linewidth]{rviz-sandtray}
    \hspace{0.2em}
    \includegraphics[width=0.48\linewidth]{3d-point-cloud-facial-features}
    \caption{The freeplay sandbox, visualised at runtime with ROS RViz. The
    poses of the interactive items are published (visible in the central panel,
    right picture), as well as an estimate of the children's head pose.  The
    left picture shows a reconstructed 3D point cloud of one child face, along
    with the detected 68 facial features.}

    \label{fig|rviz}
\end{figure}

\paragraph{Software}
The sandbox is implemented with two frameworks: the Qt's QtQuick framework
for the graphical interface of the game, and the \emph{Robot Operating System}
(ROS) for the modular implementation of the data processing and data acquisition
pipelines. A dedicated bridge between QtQuick and ROS has been specifically
developped to enable the game interface to export the positions of every
iteractive items as they move, the background image whenever it is painted over,
and the children's touches. The game interface is open-source and available online:
\url{https://github.com/severin-lemaignan/freeplay-sandbox-qt}.

@@

\subsection{Data post-processing}
\label{postprocessing}
